\projectname: A systematic search for transits in \KT\ data

### 2015-01-28 ms.tex
outline text

@@

...The future is \tess (cite something); everything we do here is
highly relevant to that important mission!

>>>>

...put in a warning here about \foreign{a priori} ``fit and subtract''
or ``correction'' of light curves.  These methods are very sensitive
to over-fitting in general, so either the investigator must
artificially restrict the model freedom or else do clever
data-censoring methods to avoid it (cite Dun AAS and in prep here).

...DFM: DOES THIS METHOD MARGINALIZE OUT THE SYSTEMATICS?  (It could,
right, because the mean and variance of the Gaussian likelihood are
analytic (though maybe expensive).)  If we \emph{do} marginalize (or
maybe either way), we need to emphasize here the difference between
simultaneously \emph{estimating} the signal and the noise as opposed
to simultaneously \emph{fitting} the signal and the noise and
marginalization out of the latter.  Key idea: Don't come to a
conclusion about (estimate) anything you don't care about, if you can
possibly avoid it!

@@

...our goals are to find new exoplanets, to generate targets for
ground-based and space-based (JWST, even) follow-up, and to understand
the full population of exoplanets.  We (as a community) have made
progress on all these fronts, but there is much more to do.

...The future is \tess\ (cite something); everything we do here is
highly relevant to that important mission!
